---
title: "R_reproducibility"
author: "Nhung"
date: "2025-04-01"
output: html_document
---

```{r setup, include = FALSE}

# required packages for reproducibility in R
library(here)
library(renv)
library(rticles)
library(devtools)
library(roxygen2)
library(gitcreds)

library(rrtools)
library(tinytex)
library(usethis)

# test the configuration for git/github/Rstudio
usethis::create_github_token() 
gitcreds::gitcreds_set()
usethis::gh_token_help()
usethis::git_sitrep()

```
## Reproducibility (for research findings)

*Reproducibility means obtaining the same result by someone else given the same data and code.*

Robustness (durableness) means obtaining the same result from the same data using a different method. Exp: using different stats method on the same data to have the same conclusion on a hypothesis.

Replicability (of a research finding on different datasets) means obtaining the same result from an independent dataset using the same method. Exp: using the same bioinformatic pipeline on different datasets to achieve a same cataloge of mutations for Mtb.

Note for "here" package to make portable paths: to create absolute paths which runs the codes from paths that are relative to the root directory (a way to declare where the root directory is), using in 2 situations: 

(1) to fix the inconsistency of root directory during knit as knitting will automatically define the root working directory being the location of the knitted file, so here:here() will help to redefine the root directory by providing its relative path; 

(2) working with a script not inside the current project, so here::i_am() function will help to declare the relative path of the scritp to the its root project.

```{r }
# testing
```





```{r cars, echo = FALSE}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
